---
title: "Test 2"
author: "M. Schonhoeft"
date: "6/26/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Test 2

Repo can be found here. <https://github.com/mitchelly00/test_2.git>.

#### Question 1 cleaning the global enviroment

```{r}
rm(list = ls())
```


#### Question 2 loading the inequality package

```{r pressure, echo=TRUE}
library(rio)
inequality_data<- import("inequality.xlsx", which=1)
```

#### Question 3 This is a Cross-sectional dataset

- It is cross sectional because as you can see in the summary that the only year is 2015
```{r,echo=TRUE}
summary(inequality_data)
```


#### Question 4 finding the gini using subset

```{r}
subset(inequality_data,country=="Denmark")
subset(inequality_data,country=="Sweden")
```


#### Question 5 finding the gini of Brazil
```{r}
subset(inequality_data,country=="Brazil")
```


#### Question 6 

It is better to have a **low** inquality_gini score as seen by the lower Scandinavian countries. 

#### Question 7 Quick peak 
```{r}
head(inequality_data)
```

#### Question 8 taking of the accent
```{r}
accent.remove<- function(s){
    #1character subsitutions
    old1<- "ú"
    new1<- "u"
    s1 <- chartr(old1,new1,s)
  }

inequality_data$country <- accent.remove(inequality_data$country)
```

Quick peak to make sure it is gone

```{r}
head(inequality_data)
```

#### Question 9 Sort the data to see which are the lowest scores 
The head comand allows us to see what the top 5 countries are

```{r}
inequality_data = inequality_data[order(inequality_data$inequality_gini),]
head(inequality_data)
```


#### Question 10 the mean inequaility_gini score
na.rm is used to take out missing values
```{r}
mean(inequality_data$inequality_gini,na.rm = TRUE)
```

#### Question 11 using ifelse command 
```{r}
inequality_data$low_high = NA
inequality_data$low_high[inequality_data$inequality_gini >= 36.81]=0
inequality_data$low_high[inequality_data$inequality_gini< 36.81]=1

ifelse(test = inequality_data$low_high==1,
       yes = "low_inequality",no = "high_inequality")
```


#### Question 12 

#### Question 13

```{r}
names<-c("The World Bank", "African Development Bank","the Bill and Melinda Gates Foundation")
```


#### Question 14
I think there is a correlation between inflation and inequaility. If there is higher inflation then the government is doing a poor job of regulating the economy which would cause inequality to increase. 

#### Question 15 inserting the data
```{r}
library(WDI)
inflation_ds =WDI(country = "all",indicator = "NY.GDP.DEFL.KD.ZG",
                     # indicator from web
                     start = 2015, end = 2015, 
                     extra = FALSE, cache = NULL)
```

#### Question 16 the new name of the variable
```{r}
library(data.table)
setnames(inflation_ds,"NY.GDP.DEFL.KD.ZG","inflation")
```

#### Question 17 merging the data frames
```{r}
library(tidyverse)
inflation_ds$year=as.numeric(inflation_ds$year)

merged_df = left_join(x=inequality_data,y=inflation_ds,
                       by=c("iso2c","year"))
```

take away the country.x
```{r}
merged_df<-
  merged_df %>% 
  select(-c("country.x")) %>% 
  dplyr::rename("country"="country.y")
```

#### Question 18 removing the NAs
```{r}
merged_df=na.omit(merged_df, select=c("inequality_gini","inflation"))
summary(merged_df)
```

#### Question 19 only keeping data greater than 30
```{r}
data_greater_30 <-
  merged_df%>%
  dplyr::filter(!(inequality_gini > 30))
```


#### Question 20 using data_greater_30 to see which countries have ai in their name
```{r}
grep("ai", data_greater_30$country)
```

#### Question 21
```{r}
sapply(data_greater_30$inequality_gini, sum)
```

#### question 22
```{r}
library(labelled)
var_label(data_greater_30)<-list(`country`="country" ,
                             `year` = "year" ,
                             `inequality_gini` =
                               "gini inequaility index" ,
                             `iso2c` = "ISO-2 country code" ,
                             `inflation` = "percent inflation of every country" ,
                             `country` = "country")
```
#### Question 23
```{r}
library(rio)
export(data_greater_30,"clean_dataset.dta")
```



